---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# rtwb-flyway

<!-- badges: start -->

<!-- badges: end -->

This dashboard is currently deployed at <https://tailwinds.umces.edu/rtwb-flyway>.

## What is this?

Use [R targets](https://docs.ropensci.org/targets/) and GitHub Actions continuous integration to plot WHOI near-real-time whale buoy (RTWB) detections for various species in the Mid-Atlantic Flyway.

Basically, an in-house version of <https://whalemap.org/> that also includes fin, sei, and humpback whales.

Dashboard is updated every day at 05:00 UTC or on demand. The last run occurred at `r format(targets::tar_meta(names = "whale_detections")$time, "%Y-%m-%d %H:%M:%S", tz = "UTC")`.

## Data sources

-   RTWB
    -   <http://robots4whales.whoi.edu/>
-   Natural Earth
    -   <https://www.naturalearthdata.com/http//www.naturalearthdata.com/download/110m/physical/ne_110m_land.zip>
-   USA NARW critical habitat
    -   <https://noaa.maps.arcgis.com/home/item.html?id=3115892b737a447abe2affa7e773701c>
-   CAN NARW critical habitat
    -   <https://open.canada.ca/data/en/dataset/db177a8c-5d7d-49eb-8290-31e6a45d786c>
-   NOAA NARW seasonal management areas
    -   <https://www.fisheries.noaa.gov/resource/map/north-atlantic-right-whale-seasonal-management-areas-sma>\
-   Slow zones

## Desired output

-   Table with columns:
    -   date
    -   species
    -   detected
    -   slow_zone_id
    -   slow_zone_active
-   Figures (5; 4 facets, 1 per species):
    -   All:
        -   [x] Coastline in OMERC projection
        -   [x] Critical habitat polygons
    -   Yesterday: 4 plots, 1 per species
        -   RTWB location filled if present, point if absent
        -   slow zone polygon filled if active, transparent if not
    -   2 days ago
    -   One-week running mean
    -   Two-week running mean
    -   One-month running mean

## Example plot

```{r, echo=FALSE, message=FALSE, warning=FALSE}
targets::tar_read(yesterday)
```

## Repository `targets` workflow:

```{r, echo=FALSE, results="asis"}
cat(c("``` mermaid", targets::tar_mermaid(), "```"), sep = "\n")
```

