---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# rtwb-flyway

<!-- badges: start -->
<!-- badges: end -->

Use GitHub Actions continuous integration to plot WHOI near-real-time whale buoy (RTWB) detections for various species in the Mid-Atlantic Flyway.

## Data sources
  -   RTWB
      -   <http://robots4whales.whoi.edu/>
  -   Natural Earth
      -   <https://www.naturalearthdata.com/http//www.naturalearthdata.com/download/110m/physical/ne_110m_land.zip>
  -   USA NARW critical habitat
      -   <https://noaa.maps.arcgis.com/home/item.html?id=3115892b737a447abe2affa7e773701c>
  -   CAN NARW critical habitat
      -   <https://open.canada.ca/data/en/dataset/db177a8c-5d7d-49eb-8290-31e6a45d786c>
  -   Slow zones

## Desired output
  -   Table with columns:
      -   date
      -   species
      -   detected
      -   slow_zone_id
      -   slow_zone_active
  -   Figures (5; 4 facets, 1 per species):
      -   All:
          -   Coastline in OMERC projection
          -   Critical habitat polygons
      -   Yesterday: 4 plots, 1 per species
          -   RTWB location filled if present, point if absent
          -   slow zone polygon filled if active, transparent if not
      -   2 days ago
      -   One-week running mean
      -   Two-week running mean
      -   One-month running mean

```{r, echo=FALSE, message=FALSE, warning=FALSE}
source('map.R')

ggplot() +
  geom_sf(data = coastline) +
  geom_sf(data = rtwb_locations) +
  geom_sf(data = narw_usa, fill = 'pink', color = NA, alpha = 0.5) +
  coord_sf(xlim = c(-1e5, 3e5),
           ylim = c(-5e5, 6e5),
           crs = projection) +
  theme_minimal() 
```

